\begin{frame}\frametitle{1}

\begin{block}{What were the most difficult parts of Anymalign to
understand?}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The transaction prob / lexical weight part.
\end{itemize}

\end{block}

\begin{block}{Why (because too many versions, because too many papers,
etc.)?}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Because I didn't realize the \textbf{one-to-many} thing at first.
\end{itemize}

\end{block}

\end{frame}

\begin{frame}\frametitle{2}

\begin{block}{What are the advantages of Anymalign over other
subsentential alignment tools or techniques?}

\begin{itemize}
\item
  not even trying to depend on huge data
\item
  solid theoretical use of hapax
\item
  memory conservative
\item
  scalable to multiple processes, even computers
\end{itemize}

\end{block}

\begin{block}{Can you name some of these tools or techniques?}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Giza++
\item
  grow-diag-final
\end{itemize}

\end{block}

\end{frame}

\begin{frame}\frametitle{3}

\begin{block}{The ultimate goal is to have Anymalign do a better job
than Giza++/Moses in conjonction with the Moses SMT engine builder.}

\end{block}

\begin{block}{Can you suggest how to achieve this goal?}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  run more instances of anymalign, and merge the alignments afterward
\end{itemize}

\end{block}

\begin{block}{Can you justify your suggestion?}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  anymalign
\end{itemize}

\end{block}

\end{frame}

\begin{frame}\frametitle{4}

Anymalign has been designed for subsentential alignment

Can you imagine other applications of Anymalign, possibly in totally
unrelated domains?

the kernel idea is ``collocation'' in NLP: unsupervised phrase mining?

\end{frame}
