\begin{frame}\frametitle{1}

\begin{block}{What were the most difficult parts of Anymalign to
  understand?}

  \begin{itemize} \itemsep1pt\parskip0pt\parsep0pt
  \item
  The transaction prob / lexical weight part.
  \end{itemize}

  \end{block}

  \begin{block}{Why (because too many versions, because too many papers,
      etc.)?}

  \begin{itemize} \itemsep1pt\parskip0pt\parsep0pt
  \item
  Because I didn't realize the \textbf{one-to-many} thing at first.
  \end{itemize}

  \end{block}

  \end{frame}

  \begin{frame}\frametitle{2}

  \begin{block}{What are the advantages of Anymalign over other
    subsentential alignment tools or techniques?}

    \begin{itemize}
    \item
    not even trying to depend on huge data
    \item
    theoretical basis on handling of hapax
    \item
    scalable to multiple processes, even computers
    \end{itemize}

    \end{block}

    \begin{block}{Can you name some of these tools or techniques?}

    \begin{itemize} \itemsep1pt\parskip0pt\parsep0pt
    \item
    Giza++
    \item
    grow-diag-final
    \end{itemize}

    \end{block}

    \end{frame}

    \begin{frame}\frametitle{3}

    \begin{block}{The ultimate goal is to have Anymalign do a better job
      than Giza++/Moses in conjunction with the Moses SMT engine builder.}

      \end{block}

      \begin{block}{Can you suggest how to achieve this goal?}

      \begin{enumerate} \itemsep1pt\parskip0pt\parsep0pt
      \item
      find a job / situation, in which anymalign can do better
      \item
      run more instances of anymalign, and merge the results
      \end{enumerate}

      \end{block}

      \begin{block}{Can you justify your suggestion?}

      \begin{enumerate} \itemsep1pt\parskip0pt\parsep0pt
      \item
      Build an corpus dedicated to evaluation set , with anymalign .
      \\ Then exploit it, for an ``adhoc translation table'',  possibly with anymalign .
      \\ The table can be used to translate evaluation set.
      \item
        being ``memory conservative'' suggests ``not making use of all memory'', so ...
      \end{enumerate}

      \end{block}

      \end{frame}

      \begin{frame}\frametitle{4}

      \begin{block}{
        Anymalign has been designed for subsentential alignment
      }
\end{block}

\begin{block}{
  Can you imagine other applications of Anymalign, possibly in totally
    unrelated domains?}{
    \begin{itemize} \itemsep1pt\parskip0pt\parsep0pt
    \item
    ``finding collocation in small sample''
    \item
    unsupervised phrase mining, in monolingual corpus?
    \item
    estimate correlation of factors, in huge data
    \end{itemize}
}
\end{block}



\end{frame}
